Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-16 doc/manuscript/ESSDmanuscript.Rmd
section 3

Previous versions of ForC [@refs] contained most of the information required for transfer to EFDB, and, more broadly, to inform C accounting under IPCC guidelines. 
However, modest changes to the structure and contents of ForC were needed in order to provide all information fequired by EFDB and to improve ForC's capacity to serve as a repository of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of the ForC database, we added ## new fields, defined ## new variables, implemented some modest restructuring (Table ##), resolved duplicate records, and conducted quality control.
This section describes changes relative to ForC v2.0 [@anderson-teixeira_forc_2018].

## Adding new fields

## Defining new variables

@@

## Resolving duplicates

Because ForC v4.0 contained known duplicate records, we used R scripts to remove likely duplicates, as detailed in @anderson-teixeira_carbon_2021.
Henceforth, we refer to the records with duplicates removed as "independent records".

@@

>>>>

Previous versions of ForC [@refs] contained most of the information required for transfer to EFDB, and, more broadly, to inform C accounting under IPCC guidelines. 
However, modest changes to the structure and contents of ForC were needed in order to provide all information fequired by EFDB and to improve ForC's capacity to serve as a repository of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of the ForC database, we added or modified ## fields (Table ##), defined ## new variables, implemented enhanced quality control, manually reviewed ># records to obtain additional required information, and added # new records.

*This section describes changes relative to ForC v2.0 [@anderson-teixeira_forc_2018].*

## New or modified fields

## New variables

@@

Because ForC v4.0 contained known duplicate records, we used R scripts to remove likely duplicates, as detailed in @anderson-teixeira_carbon_2021.
Henceforth, we refer to the set of records with likely duplicates removed as "independent records".
All records sent to EFCB were ensured to be original through manual review, as detailed below.

@@

## Addition of new records

### 2022-04-16 doc/manuscript/ESSDmanuscript.tex
section 3

Previous versions of ForC \citep{refs} contained most of the information
required for transfer to EFDB, and, more broadly, to inform C accounting
under IPCC guidelines. However, modest changes to the structure and
contents of ForC were needed in order to provide all information
fequired by EFDB and to improve ForC's capacity to serve as a repository
of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of
the ForC database, we added \#\# new fields, defined \#\# new variables,
implemented some modest restructuring (Table \#\#), resolved duplicate
records, and conducted quality control. This section describes changes
relative to ForC v2.0 \citep{anderson-teixeira_forc_2018}.

\subsection{Adding new fields}

\subsection{Defining new variables}

@@

\subsection{Resolving duplicates}

Because ForC v4.0 contained known duplicate records, we used R scripts
to remove likely duplicates, as detailed in
\citet{anderson-teixeira_carbon_2021}. Henceforth, we refer to the
records with duplicates removed as ``independent records''.

@@

>>>>

Previous versions of ForC \citep{refs} contained most of the information
required for transfer to EFDB, and, more broadly, to inform C accounting
under IPCC guidelines. However, modest changes to the structure and
contents of ForC were needed in order to provide all information
fequired by EFDB and to improve ForC's capacity to serve as a repository
of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of
the ForC database, we added or modified \#\# fields (Table \#\#),
defined \#\# new variables, implemented enhanced quality control,
manually reviewed \textgreater\# records to obtain additional required
information, and added \# new records.

\emph{This section describes changes relative to ForC v2.0
\citep{anderson-teixeira_forc_2018}.}

\subsection{New or modified fields}

\subsection{New variables}

@@

Because ForC v4.0 contained known duplicate records, we used R scripts
to remove likely duplicates, as detailed in
\citet{anderson-teixeira_carbon_2021}. Henceforth, we refer to the set
of records with likely duplicates removed as ``independent records''.
All records sent to EFCB were ensured to be original through manual
review, as detailed below.

@@

\subsection{Addition of new records}
